Web Service Wrapping, Discovery and Consumption --- More Power to the End-User

### 2010-06-14 trunk/papers/icsoc2010/paper_ssec_linked_data.tex
reduced content
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@858 d8b0c59b-6544-0410-94d9-83a5658a058e

In order to understand how content negotiation is implemented in the catalogue, a few concepts need to be understood. The URI of a particular building block must be understood as the identifier of the building block as such, as opposed to a particular representation (JSON, HTML, etc.) of it. In fact, each such representation has its own URI, under which it can be retrieved. Using the terminology established in \cite{w3c2004webArchitecture}, the building block is a \emph{non-information resource}, whereas each representation is an \emph{information resource}. In the process of content negotiation, the requesting agent will first request the URI of the building block as such (e.g., \texttt{http://catalogue.com/screens/235}), as well as the required representation format (e.g., JSON). The catalogue will then inspect the request and redirect the requester to the appropriate representation (e.g., \texttt{http://catalogue.com/screens/235.json}), as illustrated in Fig.~\ref{fig:content_negotiation}.
On the web, different representations for the same resource are called \emph{variants}, and content negotiation is the mechanism used to determine which of the representations of most appropriate for a given request.

%\begin{figure}[htb]
%\label{fig:content_negotiation}
%\begin{center}
%	\includegraphics[width=12cm]{images/content_negotiation}
%	\caption{Content Negotiation}
%\end{center}
%\end{figure}

In summary, the basic idea of content negotiation, as stated in the \cite{http1.1}, is to serve the best variant for a resource, taking into account what variants are available, what variants the server may prefer to serve, what the client can accept, and with which preferences. In HTTP, this is done by the client which may send, in its request, accept headers (\texttt{Accept}, \texttt{Accept-Language} and \texttt{Accept-Encoding}), to communicate its capabilities and preferences in format, language and encoding, respectively.

In fact, what the catalogue really does is ``format negotiation'' since the alternate representations are just based on the selection of the media type, through the accept header, but does not consider different languages or encoding types. The formats supported are JSON, RDF/XML, Turtle and HTML+RDFa. Even though the accept header is desired, the different representations can also be retrieved directly by dereferencing their own URI. The convention used in the catalogue for deriving a representation URI from a building block URI is to simply attach a matching suffix, such as \texttt{.rdf}, \texttt{.json} or \texttt{.html}.

Lastly, content negotiation needs to identify which player is going to take the lead on it. There are two kinds of content negotiation which are possible in HTTP: server-driven and agent-driven negotiation. The approach followed by the catalogue is agent-driven negotiation, hence selecting a specific representation for a resource is responsibility of the user agent. If none is specified, by default, the server will choose the JSON representation.

>>>>

To allow a third-party application to retrieve the content in the format required, we support content negotiation as stated in the \cite{http1.1}, serving the best variant for a resource, taking into account what variants are available, what variants the server may prefer to serve, what the client can accept, and with which preferences. In HTTP, this is done by the client which may send, in its request, accept headers (\texttt{Accept}, \texttt{Accept-Language} and \texttt{Accept-Encoding}), to communicate its capabilities and preferences in format, language and encoding, respectively. Concretely, the approach followed is agent-driven negotiation, where the user agent selects the specific representation for a resource.
